Setting up Data

### 2020-06-12 src/SetupData.Rmd
removing more outliers for total SC

@@

@@

#Total.SC_DF

@@

#look at date of imaging affects on total SC
#count=1
#for(i in MLH1_data$Original.Name){
   # print(i)
#    templist= strsplit(i, split="_")[[1]]
#    c = (templist[1])
#    MLH1_data$image.string[count] <-  c
    #mini$image.date[count] <-  as.Date(c, format='%d%b%y')  #"%d%b%y")
#    count= count +1
#}
#works better if dat is converted out of image
#MLH1_data$date.imaged <- as.Date(MLH1_data$image.string,  format='%d%b%y')

>>>>

Total.SC_DF <- Total.SC_DF[Total.SC_DF$subsp != "other", ]

@@

#last outliers
#Total.SC_DF <- Total.SC_DF[Total.SC_DF$skel_size < 10000, ]#one very high female measure
#Total.SC_DF <- Total.SC_DF[Total.SC_DF$skel_size < 1900, ]

Total.SC_DF.OG <- Total.SC_DF

#Total.SC_DF
tot.SC_old.mice.DF <- Total.SC_DF[Total.SC_DF$mouse  %in% old.mice.list, ]#581 lines from old mice
tot.SC_juvi.mice.DF <- Total.SC_DF[ Total.SC_DF$mouse  %in% juvi_mice.list, ]#118 lines from juvi mice

Total.SC_DF <- Total.SC_DF[! Total.SC_DF$mouse  %in% old.mice.list, ] 
Total.SC_DF <- Total.SC_DF[! Total.SC_DF$mouse  %in% juvi_mice.list, ]

```{r total.SC.outliers, echo=FALSE, eval=FALSE}

#yy <- Total.SC_DF %>% filter(subsp == "Dom") %>% filter(sex == "male")
Total.SC_DF %>% filter(subsp == "Dom") %>% filter(sex == "male")

show.total.SC <- ggplot(data= Total.SC_DF %>% filter(strain == "SKIVE"), aes(y = skel_size, x=sex, color=strain))+
  scale_color_manual(values=colors_of_strains)+
  geom_jitter() +ylim(c(950,3500 ))+ facet_wrap(~mouse, scales="free")

 # geom_boxplot(alpha=.2)+   facet_wrap(~REDO.crop, scales="free", ncol = 3) +  #geom_hline(data =totSC.strain.av.table, aes(yintercept=mean.skel) )+

  #theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), axis.line = element_line(colour = "black"),
   # axis.title.x=element_blank(),
#axis.text.x = element_text(size=7), 
#legend.position="none",axis.text.y = element_text(size=9), # axis.text.y = element_blank()
#axis.title.y = element_text(size = 10) ) +

 # labs(y = "Total SC Length")+ylim(c(1000,5000 ))+ggtitle("")

@@

@@
